
```{r}
library(RColorBrewer)
```

Scatterplot animation of population vs. co2, axes scaled logarithmically

```{r}
plot_test <- CO2_data %>%   
  #filter(year > 1970) %>% 
  ggplot(aes(x = population, y = co2)) + 
  geom_point(color = "#934583") + 
  scale_x_continuous(trans='log10') +
  scale_y_continuous(trans='log10') +
  #ylim(0, 500)+
  #xlim(0, 100000000)+
  transition_states(year)+
  labs(title = "Year: {closest_state}")
```
```{r}
animate(plot_test, renderer = gifski_renderer())

anim_save(filename = "plot_test_log.gif", animation = plot_test, path = NULL)
```

Scatterplot animation of population vs. co2

```{r}
plot_test <- CO2_data %>%   
  #filter(year > 1970) %>% 
  ggplot(aes(x = population, y = co2)) + 
  geom_point(color = "#332104") + 
  #scale_x_continuous(trans='log10') +
  #scale_y_continuous(trans='log10') +
  #ylim(0, 500)+
  #xlim(0, 100000000)+
  transition_states(year)+
  labs(title = "Year: {closest_state}")
```
```{r}
animate(plot_test, renderer = gifski_renderer())

anim_save(filename = "plot_test_follow.gif", animation = plot_test, path = NULL)
```

Histogram animation of co2 emissions over time 
```{r}
hist_test <- CO2_data %>%   
  #filter(year == 2020) %>% 
  ggplot(aes(x = co2)) + 
  geom_histogram(binwidth = 200) +
  transition_states(year)+
  labs(title = "Year: {closest_state}")
```
```{r}
animate(hist_test, renderer = gifski_renderer())

anim_save(filename = "histogram.gif", animation = hist_test, path = NULL)
```

Data tangent we could go on:
Graphing a histogram of co2 per capita over time, you can see some strong outliers from ~1950-1980. What are these countries and why are their values so high?
```{r}
hist_test_per_cap <- CO2_data %>%   
  filter(year > 1900) %>% 
  ggplot(aes(x = co2_per_capita)) + 
  geom_histogram(binwidth = 10) +
  transition_states(year) +
  labs(title = "Year: {closest_state}")
```
```{r}
animate(hist_test_per_cap, renderer = gifski_renderer(), fps = 5)

anim_save(filename = "histogram_per_cap.gif", animation = hist_test_per_cap, path = NULL)
```
Creating a dataset of them like this shows that the offenders are Brunei, Curacao, Kuwait, Quatar, Sint Maarten, and UAE. What in their history caused this?
```{r}
highC <- CO2_data %>% 
  filter(co2_per_capita > 50) %>% 
  view()
```


```{r}
CO2_data %>%   
  filter(year == 2020) %>% 
  ggplot(aes(x = population, y = co2_per_capita)) + 
  scale_x_continuous(trans='log10') +
  geom_point(color = "#332104")
```
```{r}
CO2_data %>%   
  #filter(year == 2020) %>% 
  ggplot(aes(x = population, y = co2_per_gdp)) + 
  #scale_x_continuous(trans='log10') +
  ylim(0,5) +
  geom_point(color = "#332104")

```
```{r}
co2gdp <- CO2_data %>%   
  filter(year > 1850) %>% 
  ggplot(aes(x = population, y = co2_per_gdp)) + 
  scale_x_continuous(trans='log10') +
  ylim(0,5) +
  geom_point(color = "#332104") +
  transition_states(year) +
  labs(title = "Year: {closest_state}")
```
```{r}
animate(co2gdp, renderer = gifski_renderer())

anim_save(filename = "co2gdp.gif", animation = co2gdp, path = NULL)
```

```{r}
CO2_data %>% 
  ggplot(aes(x = year, y = co2, color = country)) +
  guides(color = FALSE) +
  scale_fill_viridis_b() +
  geom_point(alpha = 0.5)
```
```{r}
timePlot <- CO2_data %>% 
  ggplot(aes(x = year, y = co2, color = country)) +
  #guides(color = FALSE) +
  scale_fill_viridis_b() +
  geom_path(alpha = 0.5) +
  geom_point(alpha = 0.5) +
  transition_reveal(along = year)
  #labs(title = "Year: {closest_state}")
```
```{r}
animate(timePlot, renderer = gifski_renderer(), end_pause = 20)

anim_save(filename = "timePlot.gif", animation = timePlot, path = NULL)
```

```{r}
timePlotpop <- CO2_data %>% 
  ggplot(aes(x = year, y = population, color = country)) +
  #guides(color = FALSE) +
  scale_fill_viridis_b() +
  geom_path(alpha = 0.5) +
  geom_point(alpha = 0.5) +
  transition_reveal(along = year)
  #labs(title = "Year: {closest_state}")
```
```{r}
animate(timePlotpop, renderer = gifski_renderer(), end_pause = 20)

anim_save(filename = "timePlotpop.gif", animation = timePlotpop, path = NULL)
```
