---
title: "Project proposal"
author: "The Emitters"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
```

## 1. Introduction

We will be attempting to create a visual representation of different countries carbon emissions per capita over time. To do this we will create a map of the world coloured by each country. The different colours of each country will represent the different levels of CO2 emissions per capita and we will animate the the visualization so that we can see the how the different emission levels change over time from 1850 on wards.

We will be using data from the owid-co2-data data set which is a massive archive of global carbon emissions data from many different sources, but we will only be looking at the following variables: country, year, population, co2, and co2 per capita.

Data citations:

owid-co2-data was created using pre-existing data from the following sources: 
BP, EIA (Energy Information Administration), Global Carbon Project, Our World In Data, and the University of Groningen GGDC's Maddison Project Database.


## 2. Data

```{r}
# Our_co2_dataset <- co2_data %>% 
#    select("country", "year", "population", "co2", "co2_per_capita")
# ```
# ```{r}
# glimpse(Our_co2_dataset)
```


## 3. Data analysis plan

  We will be visualizing the emissions rate in different countries on a world map with countries delineated and filled, representing the magnitude of emissions with a color spectrum that will change from 1950 to 2021. Countries and conglomerations of countries will be analyzed; some examples are the Asian continent without China and India or high- and low-income countries as different cases. For our variables, we have chosen to visually represent the emissions of Carbon Dioxide(CO2), Methane (CH4), Nitrous Oxide (N2O), and CO2e; our dataset contains the total population by country per year, and we will be divided emissions into total and per capita emissions.  Density stacked and ridgeline charts will be used to represent the variation of emission over time for different countries on a global and continental scale, showing the proportion of countries with the highest emissions in a designated area. 
The countries in our data set don’t have a variable with the information of which continent they are located, so we would need to add another dataset with this information to easily group them by continent. On the same note, our dataset doesn’t contain information if a country has decided to set a net-zero emissions goal or if it had proposed a reduction of total emissions, and visually represent whether the countries are on track to achieve their goal, or if their proposed goal are skewed. 


