---
title: "Project proposal"
author: "The Emitters"
output: html_document
--- 

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
```

## 1. Introduction

We will be attempting to create a visual representation of different countries carbon emissions per capita over time. To do this we will create a map of the world coloured by each country. The different colours of each country will represent the different levels of CO2 emissions per capita and we will animate the the visualization so that we can see the how the different emission levels change over time from 1850 on wards.

We will be using data from the owid-co2-data data set which is a massive archive of global carbon emissions data from many different sources, but we will only be looking at the following variables: country, year, population, co2, and co2 per capita.

Data citations:

owid-co2-data was created using pre-existing data from the following sources: 
BP, EIA (Energy Information Administration), Global Carbon Project, Our World In Data, and the University of Groningen GGDC's Maddison Project Database.


## 2. Data

```{r}
Our_co2_dataset <- owid_co2_data %>% 
   select("country", "year", "population", "co2", "co2_per_capita")
```
```{r}
glimpse(Our_co2_dataset)
```


## 3. Data analysis plan



